---
title: "Text as Data HW 1"
author: "Your Name and NetID"
date: "2/18/2020"
output: pdf_document
---


# See the HW 1 assignment for the full instructions about formatting your homework submission. Some reminders:

## Make sure your Markdown output shows both CODE and OUTPUT.

## If you write a function to use in multiple question parts, you only need to include the function definition one time. If you load data, create a variable, etc, that you use in multiple question parts, you only need to load the data or create the variable one time.

## Do NOT include written answers as code comments in code chunks.

## Using this template is not required.

------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=TRUE}
# import libraries
library(quanteda)
library(quanteda.corpora)
```

## Q1a

```{r echo=TRUE}
# your code to compute the answer
# ** Make sure your markdown document shows both CODE and OUTPUT **
print("hello")
```

Your written answer goes here.

## Q1b

```{r echo=TRUE}
# your code 
print(1+2)
```

Your written answer to Q1b goes here.
